Tropopause Evolution in a Rapidly Intensifying Tropical Cyclone: A Static Stability Budget Analysis

### 2018-01-10 paper.tex
Added radiation and eddy diffusivity figures and changed figures to run12.

%FIGURE 2%
\begin{figure}[ht]
\centerline{\includegraphics[width=33pc]{figures/mod+bud+res.png}}
\caption{Left panels: Twenty-four-hour changes in squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$ 10\textsuperscript{-4} s\textsuperscript{-2}) over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, (d) 72-96 hours. Middle Panels: The $N^2$ change over the same time periods computed using Eq. \ref{eq:budgetchange}. Right Panels: The budget residual over the same time periods, computed by subtracting the budget change (middle column) from the model change (left column).}
\label{fig:mod+bud+res}
\end{figure}

@@

%FIGURE 4%
\begin{figure}[ht]
\centerline{\includegraphics[width=19pc]{figures/AVG_budterms.png}}
\caption{Time series of the contribution of each of the budget terms to the time tendency of the squared Brunt-V{\"a}is{\"a}l{\"a} frequency (N\textsuperscript{2}; 10\textsuperscript{-4} s\textsuperscript{-2}). For each budget term, the absolute value of the N\textsuperscript{2} tendency is averaged temporally over 1-hour periods (using output every minute), and spatially in a region extending from 0 to 200 km radius and 14 to 19 km altitude.}
\label{fig:avgbudterms}
\end{figure}

%FIGURE 5%
\begin{figure*}[ht]
\centerline{\includegraphics[width=39pc]{figures/h000-h024-budgetterms.png}}
\caption{(a) Total change in N\textsuperscript{2} over the 0-24-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 hr)\textsuperscript{-1}) and the contributions to that change from (b) the sum of horizontal and vertical advection, (c) vertical turbulence, and (d) the sum of longwave and shortwave radiation.}
\label{fig:stab-00-24}
\end{figure*}

%FIGURE 6%
\begin{figure*}[ht]
\centerline{\includegraphics[width=39pc]{figures/h024-h048-budgetterms.png}}
\caption{As in Fig.~\ref{fig:stab-00-24}, but for the 24-48-hour period.}
\label{fig:stab-24-48}
\end{figure*}

%FIGURE 7%
\begin{figure*}[ht]
\centerline{\includegraphics[width=27pc]{figures/h048-h072-budgetterms.png}}
\caption{(a) Total change in N\textsuperscript{2} over the 48-72-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 hr)\textsuperscript{-1}) and the contributions to that change from (b) the sum of horizontal and vertical advection, (c) vertical turbulence, (d) the sum of longwave and shortwave radiation, (e) the sum of horizontal advection, vertical advection, and vertical turublence, and (f) the sum of horizontal advection, vertical advection, vertical turbulence, and longwave and shortwave radiation.}
\label{fig:stab-48-72}
\end{figure*}

%FIGURE 8%
\begin{figure*}[ht]
\centerline{\includegraphics[width=33pc]{figures/h072-h096-budgetterms.png}}
\caption{As in Fig.~\ref{fig:stab-48-72}, but for the 72-96-hour period.}
\label{fig:stab-72-96}
\end{figure*}

%FIGURE 9%
\begin{figure*}[ht]
\centerline{\includegraphics[width=39pc]{figures/u.png}}
\caption{Radial velocity (m s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold point tropopause height (orange line) averaged over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours.}
\label{fig:u}
\end{figure*}

%FIGURE 10%
\begin{figure*}[ht]
\centerline{\includegraphics[width=39pc]{figures/w.png}}
\caption{Vertical velocity (cm s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold point tropopause height (orange line) averaged over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours.}
\label{fig:w}
\end{figure*}

%FIGURE 11%
\begin{figure*}[ht]
\centerline{\includegraphics[width=39pc]{figures/qtot.png}}
\caption{Total condensate mixing ratio (g kg\textsuperscript{-1}) and cold point tropopause height (orange line) averaged over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours.}
\label{fig:qtot}
\end{figure*}

%\begin{figure}[t]
%  \noindent\includegraphics[width=19pc,angle=0]{figure01.pdf}\\
%  \caption{Enter the caption for your figure here.  Repeat as
%  necessary for each of your figures. Figure from \protect\cite{Knutti2008}.}\label{f1}
%\end{figure}

>>>>

%FIGURE 2%
\begin{figure}[ht]
\centerline{\includegraphics[width=39pc]{figures/mod+bud+res.png}}
\caption{Left panels: Twenty-four-hour changes in squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$ 10\textsuperscript{-4} s\textsuperscript{-2}) over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, (d) 72-96 hours. Middle Panels: The $N^2$ change over the same time periods computed using Eq. \ref{eq:budgetchange}. Right Panels: The budget residual over the same time periods, computed by subtracting the budget change (middle column) from the model change (left column).}
\label{fig:mod+bud+res}
\end{figure}

@@

%FIGURE 4%
\begin{figure}[ht]
\centerline{\includegraphics[width=19pc]{figures/AVG_budterms.png}}
\caption{Time series of the contribution of each of the budget terms to the time tendency of the squared Brunt-V{\"a}is{\"a}l{\"a} frequency (N\textsuperscript{2}; 10\textsuperscript{-4} s\textsuperscript{-2}). For each budget term, the absolute value of the N\textsuperscript{2} tendency is averaged temporally over 1-hour periods (using output every minute), and spatially in a region extending from 0 to 200 km radius and 14 to 21 km altitude.}
\label{fig:avgbudterms}
\end{figure}

%FIGURE 5%
\begin{figure*}[ht]
\centerline{\includegraphics[width=27pc]{figures/h000-h024-budgetterms.png}}
\caption{(a) Total change in N\textsuperscript{2} over the 0-24-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 hr)\textsuperscript{-1}) and the contributions to that change from (b) the sum of horizontal and vertical advection, (c) vertical turbulence, (d) longwave and shortwave radiation, (e) the sum of horizontal advection, vertical advection, and vertical turublence, and (f) the sum of horizontal advection, vertical advection, vertical turbulence, and longwave and shortwave radiation.}
\label{fig:stab-00-24}
\end{figure*}

%FIGURE 6%
\begin{figure*}[ht]
\centerline{\includegraphics[width=27pc]{figures/h024-h048-budgetterms.png}}
\caption{As in Fig.~\ref{fig:stab-00-24}, but for the 24-48-hour period.}
\label{fig:stab-24-48}
\end{figure*}

%FIGURE 7%
\begin{figure*}[ht]
\centerline{\includegraphics[width=27pc]{figures/h048-h072-budgetterms.png}}
\caption{As in Fig.~\ref{fig:stab-00-24}, but for the 48-72-hour period.}
\label{fig:stab-48-72}
\end{figure*}

%FIGURE 8%
%\begin{figure*}[ht]
%\centerline{\includegraphics[width=33pc]{figures/h072-h096-budgetterms.png}}
%\caption{As in Fig.~\ref{fig:stab-48-72}, but for the 72-96-hour period.}
%\label{fig:stab-72-96}
%\end{figure*}

%FIGURE 8%
\begin{figure*}[ht]
\centerline{\includegraphics[width=39pc]{figures/u.png}}
\caption{Radial velocity (m s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold point tropopause height (orange lines) averaged over (a) 0-24 hours, (b) 24-48 hours, and (c) 48-72 hours.}
\label{fig:u}
\end{figure*}

%FIGURE 9%
\begin{figure*}[ht]
\centerline{\includegraphics[width=39pc]{figures/w.png}}
\caption{Vertical velocity (cm s\textsuperscript{-1}; filled contours), potential temperature (K; thick black contours), and cold point tropopause height (orange lines) averaged over (a) 0-24 hours, (b) 24-48 hours, and (c) 48-72 hours.}
\label{fig:w}
\end{figure*}

%FIGURE 10%
\begin{figure*}[ht]
\centerline{\includegraphics[width=39pc]{figures/qtot.png}}
\caption{Total condensate mixing ratio (g kg\textsuperscript{-1}) and cold point tropopause height (orange lines) averaged over (a) 0-24 hours, (b) 24-48 hours, and (c) 48-72 hours.}
\label{fig:qtot}
\end{figure*}

%FIGURE 11%
\begin{figure*}[ht]
\centerline{\includegraphics[width=39pc]{figures/radten.png}}
\caption{Radiative heating rate (K hr\textsuperscript{-1}) and cold point tropopause height (orange lines) averaged over (a) 0-24 hours, (b) 24-48 hours, and (c) 48-72 hours.}
\label{fig:radten}
\end{figure*}

%FIGURE 12%
\begin{figure*}[ht]
\centerline{\includegraphics[width=39pc]{figures/khvten.png}}
\caption{Vertical eddy diffusivity (m\textsuperscript{2} s\textsuperscript{-2}; filled contours), cold point tropopause height (cyan lines), and radial velocity (m s\textsuperscript{-1}; thick black lines) averaged over (a) 0-24 hours, (b) 24-48 hours, and (c) 48-72 hours.}
\label{fig:radten}
\end{figure*}

%\begin{figure}[t]
%\begin{figure}[t]
%\begin{figure}[t]
%  \noindent\includegraphics[width=19pc,angle=0]{figure01.pdf}\\
%  \caption{Enter the caption for your figure here.  Repeat as
%  necessary for each of your figures. Figure from \protect\cite{Knutti2008}.}\label{f1}
%\end{figure}
